---
title: "\ "
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[**click to view group 25's GitHub Repository**](https://github.com/rforbiodatascience23/group_25_package)

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# group_25_CentralDogma

This package can be used to replicate the central dogma of molecular biology. The central dogma of biology describes the flow of genetic information: DNA is transcribed into RNA, which is then translated into proteins.

Dependencies for this package: ggplot2 and stringr.

## Library Loading

```{r setup}
library(centraldogma)
```

## Function Descriptions
### generate_DNA

This function creates a random DNA sample of user-defined length (input is an integer defining DNA_length).

**Example**

```{r}
generate_DNA(10)
#> [1] "CTCCAGAGGG"
```

### transcription

Transcribes the DNA sequence to RNA by substitution of the amino acid 'T' with 'U'. The input is a DNA sequence given as a string.

**Example**

```{r}
transcription("ATCG")
#> [1] "AUCG"
```

### mRNA_to_codons

This function splits the mRNA sequence into codons. Inputs are the position at which to start at (int, Default is 1) and the mRNA sequence. It returns a list of codons.

**Example**

```{r}
# Define an illustrative mRNA sequence (replace with a real sequence when using the package)
mRNA_seq <- "AACCCGTTAAAGGATCTGTAACAATACTGGACAA"

# Use the defined mRNA sequence in the function
mRNA_to_codons(mRNA_seq)

#>  [1] "AAC" "CCC" "GTT" "AAA" "GGA" "TCT" "GTA" "AAC" "AAT" "ACT" "GGA" "CAA"
#> [13] "GAA" "TCA" "TAG" "CTA" "GCA" "TCA" "GTT" "ATG" "GTG" "AGT" "CGA" "ACA"
#> [25] "GAG" "GAA" "TCT" "TAG" "AGG" "TAT" "GCA" "AGT" "AAA"
```

### translation

The function translates from codons to amino acid sequences. Input (codons) is a list of codons to translate and output is a string of amino acid sequences.

```{r}
translation("UUU")
#> [1] "F"
```

### plot_character_frequency

This function takes a string as input and plots a bar chart showing the frequency of each unique character in the string. The plot is generated using ggplot2.

```{r, include=FALSE}
plot_character_frequency("hello")
```

### Dependencies for Function Five (plot_character_frequency)

For the function [plot_character_frequency](https://github.com/rforbiodatascience23/group_25_package/blob/master/R/plot_character_frequency.R), I used `ggplot2` for plotting and `stringr` for string manipulation. Added via `@importFrom` in Roxygen comments. By specifying the functions I need, I keep the package lightweight and reduce potential conflicts with other packages.

### Limits on the Number of Dependencies

We limited dependencies to `ggplot2` and `stringr` to keep the package lightweight and avoid conflicts. While adding more could enhance the functionality, it would also complicate the maintenance.

### Compare Approaches for Importing Functions

We chose to use `@importFrom` to import only what is needed, making the package efficient. Using `package::function()` could clutter our code, so we avoided it for clarity.
