---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# CentralDogma

This package can be used to replicate the central dogma of molecular biology. The central dogma of biology describes the flow of genetic information: DNA is transcribed into RNA, which is then translated into proteins.

Dependencies for this package: ggplot2 and stringr.

## Library Loading

```{r setup}
library(centraldogma)
```

## Function Description

------------------------------------------------------------------------

### generate_DNA

This function creates a random DNA sample of user-defined length (input is an integer defining DNA_length).

**Example**

```{r}
generate_DNA(10)
#> [1] "CTCCAGAGGG"
```

### transcription

Transcribes the DNA sequence to RNA by substitution of the amino acid 'T' with 'U'. The input is a DNA sequence given as a string.

**Example**

```{r}
transcription("ATCG")
#> [1] "AUCG"
```

### mRNA_to_codons

This function splits the mRNA sequence into codons. Inputs are the position at which to start at (int, Default is 1) and the mRNA sequence. It returns a list of codons.

**Example**

```{r}
# Define an illustrative mRNA sequence (replace with a real sequence when using the package)
mRNA_seq <- "AACCCGTTAAAGGATCTGTAACAATACTGGACAA"

# Use the defined mRNA sequence in the function
mRNA_to_codons(mRNA_seq)

#>  [1] "AAC" "CCC" "GTT" "AAA" "GGA" "TCT" "GTA" "AAC" "AAT" "ACT" "GGA" "CAA"
#> [13] "GAA" "TCA" "TAG" "CTA" "GCA" "TCA" "GTT" "ATG" "GTG" "AGT" "CGA" "ACA"
#> [25] "GAG" "GAA" "TCT" "TAG" "AGG" "TAT" "GCA" "AGT" "AAA"
```

### translation

The function translates from codons to amino acid sequences. Input (codons) is a list of codons to translate and output is a string of amino acid sequences.

```{r}
translation("UUU")
#> [1] "F"
```

### baar_count
